---
title: "Analysis_Exp1"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readxl)
library(car)
library(rstatix)
library(lmerTest)
library(effectsize)
```

# read in data

```{r}
# Summary data:
exp1_data <- read.csv("exp1_data.csv") %>%
  mutate(subject = as.factor(subject),
         group = as.factor(group))


# N-back data:


exp1_nback <- readRDS("nback_lab.RDS") # data by trial

nback_pep_long <- read_xlsx("NbackPEPbytime.xlsx") # this dataset has every PEP measurement

nback_pep <- readRDS("nback_pep.RDS") # this dataset has PEP per N-back block


# MET data

## data by trial:
exp1_met_trials <- read.csv("exp1_met_trials.csv") %>%
  rename(difficulty = currentLevel) %>%
  mutate(group = as.factor(group),
         subject = as.factor(subject),
         trialpercent = trial/50)  %>%
  select(subject, group, trial, difficulty, correct, trialpercent) %>%
  left_join(exp1_data[,c('subject', 'math_sc')])

## PEP data:
met_pep <- readRDS("met_pep.RDS")
```

# Clean data sets:

## Nback: 

```{r}

# Residualise PEP scores by Nback difficulty, average across each participant

nback_pep_ppt <- nback_pep_long %>% 
  na.omit() %>%
  mutate(subject = as.factor(subject), 
         PEPresid = rstandard(lm(PEP~ nback, data = nback_pep_long))) %>%
  group_by(subject) %>% 
  summarise(PEPresid = mean(PEPresid)) 

exp1_data <- left_join(exp1_data, nback_pep_ppt)

# calculate nback performance by block

nback_perf_blocks <- exp1_nback %>%
  filter(trialcode %in% c("target", "nontarget")) %>%
  rename(blocknum = values.TotalBlocks) %>%
  group_by(subject, blocknum) %>%
  summarise(performance = mean(correct))

# calculate how much reward was gotten in each block:

nback_rewards <- exp1_nback %>%
  filter(trialcode == "rewardtext") %>%
  rename(nback = values.N, reward = list.rewardoptions.nextvalue, blocknum = values.TotalBlocks) %>%
  select(subject, nback, reward, blocknum, group)

# combine datasets with performance, reward, pep:

nback_blocks <- left_join(nback_rewards, nback_pep[,c("subject", "blocknum", "pep")]) %>%
  left_join(nback_perf_blocks[,c("subject", "blocknum", "performance")]) %>%
  filter(subject %in% exp1_data$subject) %>%
  mutate(group = as.factor(group),
         subject = as.factor(subject),
         nback = as.factor(nback)) %>%
  left_join(exp1_data[,c("subject", "math_sc")])
```

## MET

```{r}
# calculate PEP per block in MET:
met_pep_short <- met_pep %>%
  group_by(subject, block) %>%
  summarise(pep = mean(PEP), difficulty = mean(Math, na.rm = T))


# Add column 'block' to count blocks in exp1_met_trials

exp1_met_trials$block <- NA

x <- exp1_met_trials
for (i in unique(x$subject)){
  blocknumber = 1
  count5 = 0
  x$block[x$subject == i][1] <- blocknumber #start at block number 1 for each subject
  for (j in 2:nrow(x[x$subject == i,])) {
    count5 = count5+1
    if ((count5 == 5) | (x$difficulty[x$subject == i][j] != x$difficulty[x$subject == i][j - 1])){ # if block number changes or 5 trials at given difficulty level is reached, increase block number by 1
      blocknumber = blocknumber+1
      count5 = 0
    }
    x$block[x$subject == i][j] <- blocknumber
  }
}
exp1_met_trials <- x


# find average correct on each block
met_block_performance <- exp1_met_trials %>%
  group_by(subject, group, block, difficulty) %>%
  summarise(correct = mean(correct)) 

#Join together data frames with performance and PEP data:

met_pep_df <- left_join(met_block_performance, met_pep_short) %>%
  group_by(subject) %>%
  left_join(exp1_data[,c("subject", "math_sc")])
```


# Analysis: 

# MET Difficulty choice by group:

```{r}

aov1 <- aov(difficulty ~ math_sc + group, data = exp1_data)
summary(aov1)
rstatix::eta_squared(aov1)

# without math self-concept:
aov1b <- aov(difficulty ~ group, data = exp1_data)
summary(aov)

exp1_group_difficulty_summary <- exp1_data %>%
  group_by(group) %>%
  summarise(mean = mean(difficulty), sd = sd(difficulty))

```

# Difficulty choice across time

```{r}
mod1 <- lmer(difficulty ~ math_sc + group + poly(trialpercent, 2, raw = TRUE) + poly(trialpercent,2, raw = TRUE):group
             + (trialpercent|subject), data = exp1_met_trials, REML = FALSE)
summary(mod1)
```

# PEP predicting difficulty choice

```{r}
# Group 1:
cor.test(exp1_data$difficulty[exp1_data$group == 1], exp1_data$PEPresid[exp1_data$group == 1])

# Group 2:
cor.test(exp1_data$difficulty[exp1_data$group == 2], exp1_data$PEPresid[exp1_data$group == 2])

# anova:
summary(aov(PEPresid ~ group*difficulty, exp1_data))
```


# MET group difference in effort: 

```{r}
mod2 <- lmer(pep ~ group + difficulty + block  + (block|subject), met_pep_df)
summary(mod2)
anova(mod2)
```

# MET group difference in performance, logistic multi-level model:

```{r}
mod3 <- glmer(correct ~ group + difficulty + (difficulty|subject), family = binomial("logit"), data = exp1_met_trials)
summary(mod3)
```


# Nback analysis of effort, difficulty and performance:

## Effort by block, group and difficulty:

```{r}
mod4 <- lmer(pep ~ group + blocknum + nback + (blocknum| subject), nback_blocks)
summary(mod4)
anova(mod4)
```

## Performance by block, group, difficulty

```{r}
mod5 <- lmer(performance ~ nback + group + blocknum + (blocknum|subject), nback_blocks)
summary(mod5)
anova(mod5)
```

## Performance by block, group, effort

```{r}
mod6 <- lmer(performance ~ pep + group +  blocknum + (blocknum|subject), nback_blocks)
summary(mod6)
anova(mod6)
```


# achievement motivation

```{r}
mod7 <- aov(hope_of_success ~ math_sc + group, data = exp1_data)
summary(mod7)
rstatix::eta_squared(mod7)

exp1_group_hos_summary <- exp1_data %>%
  group_by(group) %>%
  summarise(mean = mean(hope_of_success), sd = sd(hope_of_success))

```

#Baseline

```{r}
summary(lm(cbind(PreMood, PreTired, SBPBase, DBPBase, MAPBase, HRbase, PEPBase) ~ group, data = exp1_data))
effectsize::eta_squared(lm(cbind(PreMood, PreTired, SBPBase, DBPBase, MAPBase, HRbase, PEPBase) ~ group, data = exp1_data))
```

# Reward analysis

## Reward by group overall:
```{r}
mod8 <- aov(reward ~ group, data = exp1_data)
rstatix::eta_squared(mod8)

reward_group_exp1 <- exp1_data %>%
  group_by(group) %>%
  summarise(mean= mean(reward), sd = sd(reward))
```

## Reward by N-back block (manipulation check)

```{r}
mod9 <- lmer(reward~ group*pep + (pep|subject), data = nback_blocks)
summary(mod9)
anova(mod9)
```

## Nback performance predicting difficulty choice
```{r}
mod10 <- lm(difficulty ~ group*nback_performance, data = exp1_data)
Anova(mod10, type = "III")
```

# Post task questionnaires:
```{r}
# MET Level 1 enjoyment:
summary(aov(level1_response ~ group, exp1_data))
rstatix::eta_squared(aov(level1_response ~ group, exp1_data))

# MET Level 2 enjoyment:
summary(aov(level2_response ~ group, exp1_data))
rstatix::eta_squared(aov(level2_response ~ group, exp1_data))

# Willpower
summary(aov(willpower ~ group, exp1_data))
rstatix::eta_squared(aov(willpower ~ group, exp1_data))

# Remaining questionnaires:
summary(lm(cbind(level3_response, level4_response, level5_response, enjoy_response, difficulty_response, PostTired, PostMood) ~ group, data = exp1_data))
effectsize::eta_squared(lm(cbind(level3_response, level4_response, level5_response, enjoy_response, difficulty_response, PostTired, PostMood) ~ group, data = exp1_data))
```





