---
title: "Analysis_Exp1"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(car)
library(rstatix)
library(lmerTest)
library(effectsize)
```

# read in data

```{r}
# Summary data:
exp1_data <- read.csv("exp1_data.csv") %>%
  mutate(subject = as.factor(subject),
         group = as.factor(group))

# N-back data:

## trial level data:
exp1_nback <- read.csv("exp1_nback_trials.csv")

## PEP data:
nback_pep_long <- read.csv("exp1_nback_pep.csv") # this dataset has every PEP measurement


# MET data

## trial level data:
exp1_met_trials <- read.csv("exp1_met_trials.csv") %>%
  mutate(group = as.factor(group),
         subject = as.factor(subject),
         trialpercent = trial/50) %>%
  select(subject, group, trial, difficulty, correct, trialpercent, block) %>%
  left_join(exp1_data[,c('subject', 'math_sc')])


## PEP data:
met_pep <- read.csv("exp1_met_pep.csv") %>%
  mutate(subject = as.factor(subject))
```

# Clean data sets:

## Nback: 

```{r}


# Residualise PEP scores by Nback difficulty, average across each participant

nback_pep_ppt <- nback_pep_long %>% 
  na.omit() %>%
  mutate(subject = as.factor(subject), 
         PEPresid = rstandard(lm(PEP~ N, data = nback_pep_long))) %>%
  group_by(subject) %>% 
  summarise(PEPresid = mean(PEPresid)) 

exp1_data <- left_join(exp1_data, nback_pep_ppt)


# calculate nback performance by block

nback_perf_blocks <- exp1_nback %>%
  filter(trialcode %in% c("target", "nontarget")) %>%
  group_by(subject, blocknum) %>%
  summarise(performance = mean(correct))

# extract reward and PEP for each block:

nback_rewards <- exp1_nback %>%
  filter(trialcode == "rewardtext") %>%
  select(subject, N, block_reward, blocknum, group, pep)

# combine datasets with performance, reward, pep:

nback_blocks<- left_join(nback_rewards, nback_perf_blocks[,c("subject", "blocknum", "performance")]) %>%
  filter(subject %in% exp1_data$subject) %>%
  mutate(group = as.factor(group),
         subject = as.factor(subject),
         N = as.factor(N)) %>%
  left_join(exp1_data[,c("subject", "math_sc")])
```

## MET

```{r}
# calculate PEP per block in MET:
met_pep_short <- met_pep %>% 
  group_by(subject, block) %>%
  summarise(pep = mean(PEP), difficulty = mean(level, na.rm = T))


# find average correct on each block
met_block_performance <- exp1_met_trials %>%
  group_by(subject, group, block, difficulty) %>%
  summarise(correct = mean(correct)) 

#Join together data frames with performance and PEP data:

met_pep_df <- left_join(met_block_performance, met_pep_short) %>%
  group_by(subject) %>%
  left_join(exp1_data[,c("subject", "math_sc")])
```


# Analysis: 

# MET Difficulty choice by group:

```{r}

aov1 <- aov(difficulty ~ math_sc + group, data = exp1_data)
summary(aov1)
rstatix::eta_squared(aov1)

# without math self-concept:
aov1b <- aov(difficulty ~ group, data = exp1_data)
summary(aov1b)

exp1_group_difficulty_summary <- exp1_data %>%
  group_by(group) %>%
  summarise(mean = mean(difficulty), sd = sd(difficulty))

```

# Difficulty choice across time

```{r}
mod1 <-
  lmer(
    difficulty ~ math_sc + group + poly(trialpercent, 2, raw = TRUE) + poly(trialpercent, 2, raw = TRUE):group
    + (trialpercent |
         subject),
    data = exp1_met_trials,
    REML = FALSE
  )
summary(mod1)
```

# PEP predicting difficulty choice

```{r}
# Group 1:
cor.test(exp1_data$difficulty[exp1_data$group == 1], exp1_data$PEPresid[exp1_data$group == 1])

# Group 2:
cor.test(exp1_data$difficulty[exp1_data$group == 2], exp1_data$PEPresid[exp1_data$group == 2])

# anova:
summary(aov(PEPresid ~ group*difficulty, exp1_data))
```


# MET group difference in effort: 

```{r}
mod2 <- lmer(pep ~ group + difficulty + block  + (block|subject), met_pep_df)
summary(mod2)
anova(mod2)
```

# MET group difference in performance, logistic multi-level model:

```{r}
mod3 <- glmer(correct ~ group + difficulty + (difficulty|subject), family = binomial("logit"), data = exp1_met_trials)
summary(mod3)
```


# Nback analysis of effort, difficulty and performance:

## Effort by block, group and difficulty:

```{r}
mod4 <- lmer(pep ~ group + blocknum + N + (blocknum| subject), nback_blocks)
summary(mod4)
anova(mod4)

#group:
F_to_eta2(0.2059, 1, 119)

#difficulty
F_to_eta2(6.4096, 2, 1591)
```

## Performance by block, group, difficulty

```{r}
mod5 <- lmer(performance ~ N + group + blocknum + (blocknum|subject), nback_blocks)
summary(mod5)
anova(mod5)

#difficulty:
F_to_eta2(492.0742 , 2, 1678)

#group
F_to_eta2(1.2664, 1, 119)
```

## Performance by block, group, effort

```{r}
mod6 <- lmer(performance ~ pep + group +  blocknum + (blocknum|subject), nback_blocks)
summary(mod6)
anova(mod6)

#effort:
F_to_eta2(0.0044  , 1, 263)
```


# achievement motivation

```{r}
mod7 <- aov(hope_of_success ~ math_sc + group, data = exp1_data)
summary(mod7)
rstatix::eta_squared(mod7)

exp1_group_hos_summary <- exp1_data %>%
  group_by(group) %>%
  summarise(mean = mean(hope_of_success), sd = sd(hope_of_success))

```

#Baseline

```{r}
baseline_table <- exp1_data %>%
  group_by(group) %>%
  summarise(baseline_pep_mean = mean(PEPBase),
            baseline_pep_sd = sd(PEPBase),
            baseline_sbp_mean = mean(SBPBase),
            baseline_sbp_sd = sd(SBPBase),
            baseline_dbp_mean = mean(DBPBase),
            baseline_dbp_sd = sd(DBPBase),
            baseline_map_mean = mean(MAPBase),
            baseline_map_sd = sd(MAPBase),
            baseline_hr_mean = mean(HRBase),
            baseline_hr_sd = sd(HRBase))



summary(lm(cbind(PreMood, PreTired, SBPBase, DBPBase, MAPBase, HRBase, PEPBase) ~ group, data = exp1_data))
effectsize::eta_squared(lm(cbind(PreMood, PreTired, SBPBase, DBPBase, MAPBase, HRBase, PEPBase) ~ group, data = exp1_data))
```

# Reward analysis

## Reward by group overall:
```{r}
mod8 <- aov(reward ~ group, data = exp1_data)
summary(mod8)
rstatix::eta_squared(mod8)

reward_group_exp1 <- exp1_data %>%
  group_by(group) %>%
  summarise(mean= mean(reward), sd = sd(reward))
```

## Reward by N-back block (manipulation check)

```{r}
mod9 <- lmer(block_reward~ group*pep + (pep|subject), data = nback_blocks)
summary(mod9)
anova(mod9)

# group*pep interaction
F_to_eta2(4.4096, 1, 1803)
```

## Nback performance predicting difficulty choice
```{r}
mod10 <- lm(difficulty ~ group*nback_performance, data = exp1_data)
Anova(mod10, type = "III")
rstatix::eta_squared(mod10)
```

# Post task questionnaires:
```{r}

# MET Level 1 enjoyment:
summary(aov(level1_response ~ group, exp1_data))
rstatix::eta_squared(aov(level1_response ~ group, exp1_data))

# MET Level 2 enjoyment:
summary(aov(level2_response ~ group, exp1_data))
rstatix::eta_squared(aov(level2_response ~ group, exp1_data))

# MET Level 3 enjoyment:
summary(aov(level3_response ~ group, exp1_data))
rstatix::eta_squared(aov(level3_response ~ group, exp1_data))

# MET Level 4 enjoyment:
summary(aov(level4_response ~ group, exp1_data))
rstatix::eta_squared(aov(level4_response ~ group, exp1_data))

# MET Level 5 enjoyment:
summary(aov(level5_response ~ group, exp1_data))
rstatix::eta_squared(aov(level5_response ~ group, exp1_data))

# Willpower
summary(aov(willpower ~ group, exp1_data))
rstatix::eta_squared(aov(willpower ~ group, exp1_data))

# Remaining questionnaires:
summary(lm(cbind(enjoy_MET, difficulty_MET, PostTired, PostMood) ~ group, data = exp1_data))
effectsize::eta_squared(lm(cbind(enjoy_MET, difficulty_MET, PostTired, PostMood) ~ group, data = exp1_data))
```





